\textbf{Perius: A Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-23 tex/paper.tex
Reorganised findings section

As large projects most often are divided into different dividable parts, a concept called containers
is introduced in this work. Containers can contain more containers and content and when
modifying the security settings for a container it is applied recursively to all its content and
sub-containers.

@@

\subsection{Findings}
\subsubsection{Scalability}
When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enormous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak, as discussed in 
Section~\ref{sec:GET_REQUESTS}, for what Casbah can handle on a single server.

@@

>>>>

As large projects most often are divided into different dividable parts, a concept called containers
is introduced in this work. Containers can contain more containers and content, and when
modifying the security settings for a container it is applied recursively to all its content and
sub-containers.

@@

\subsection{Findings}
This section presents the relevant findings derived from the implementation and testing of it.

@@

\subsubsection{Scalability}
When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enormous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak, as discussed in 
Section~\ref{sec:GET_REQUESTS}, for what Casbah can handle on a single server.
